
\documentclass{brownhonorsthesis}

\input{author-title-etc}  % Put all the author title stuff in there

% ------
% Fonts and typesetting settings
%\usepackage[sc]{mathpazo}
%\usepackage[T1]{fontenc}
%\linespread{1.05} % Palatino needs more space between lines

%\usepackage{microtype}
% ------
% Page layout
\usepackage[labelfont=bf,labelformat=simple,labelsep=quad]{caption}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsfonts}
\usepackage{natbib}
\usepackage{subfigure}
\usepackage{xspace}
\usepackage{mathrsfs}
\usepackage{fancyhdr}
\usepackage{cuted}
\usepackage{flushend}
\usepackage{color}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{placeins}


%% some handy things for making bold math
\def\bm#1{\mathpalette\bmstyle{#1}}
\def\bmstyle#1#2{\mbox{\boldmath$#1#2$}}
\newcommand{\thh}{^\mathrm{th}}


%% Some pretty etc.'s, etc...
\newcommand{\cf}{{\em cf.}\xspace }
\newcommand{\eg}{{\em e.g.},\xspace }
\newcommand{\ie}{{\em i.e.},\xspace }
\newcommand{\etal}{{\em et al.}\ }
\newcommand{\etc}{{\em etc.}\@\xspace}



%% the page dimensions
\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = -0.01 in
\evensidemargin = -0.01 in
\topmargin = -0.7 in
\headheight = 0.25 in
\headsep = 0.25 in
\parskip = 0.0in
\parindent = 0.25in

\setlength{\columnsep}{.4in}






\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\title{Methods and software for detecting contaminated samples genotyped with SNPs}
\author{Elena N. Venable}
\dept{Applied Math}

\reader[(Applied Mathematics)]{Anastasios Matzavinos}
\reader[(Applied Mathematics)]{Bjorn Sandstede}
\dean{Name}


\beforepreface
\abstract{
Single nucleotide polymorphisms (SNPs) are genetic markers commonly used in molecular ecology.  SNP genotyping is a practical alternative to microsatellite genotyping due to lower cost, easier standardization, and abundance in species' genomes.  However, SNP genotyping lacks a standardized process for identifying contamination, and cross-contaminated DNA samples can undermine results. In this paper, I develop a model for detecting contaminated samples from SNP genotype data and test two variations of this model using \emph{in silico} data.  The simulation tests show that the model accurately identifies contaminated DNA samples and accurately estimates the contamination rate of a collection of samples. 
}
\abstractpage


\prefacesection{Acknowledgements}
I would like to thank Eric Anderson for providing support and guidance on the research and paper as well as Carlos Garza and the Molecular Ecology Team at the National Oceanic and Atmospheric Association (NOAA) Southwest Fisheries Science Center (SWFSC) for general support.  I would also like to thank the NOAA Ernest F. Hollings scholarship for providing me with funding for my research.  I also thank Anastasios Matzavinos and Bj\"{o}rn Sandstede for providing advice on the paper.


\afterpreface
\doublespacing


\input{main-body-text.Rnw}

%\appendix
%\input{appendices.Rnw}

\bibliographystyle{plain}
{\footnotesize
\bibliography{snp-contam}}
%\flushcolsend

\end{document}


